---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

Install required package for machine learning model library 
```{r}
#install.packages("openxlsx")
#install.packages("caret")
#install.packages("MLeval")
#install.packages("Metrics")
```

```{r}
library(openxlsx)
library(caret)
library(MLeval)
library(Metrics)
```

#read cleaned data and split it into 80/20, 
```{r}
regre <- read.xlsx("new.xlsx",1)
regre

split=0.80  # define an 80%/20% train/test split of the dataset
trainIndex<-createDataPartition(regre$PremiumPrice, p=split, list=FALSE)
data_train<-regre[ trainIndex,]
test_set<-regre[-trainIndex,]
train_control <- trainControl(method="repeatedcv", number=10, repeats=5)
```
K-nearest neighbors algorithm
```{r}
#knn <- train(PremiumPrice ~., data=data_train, trControl=train_control, method="knn")
#saveRDS(knn, "knn.rds")
knn<- readRDS("knn.rds")
pred_knn <- round(predict(knn, newdata=test_set),1)
```

Bayesian Ridge Regression
```{r}
#bridge <- train(PremiumPrice ~., data=data_train, trControl=train_control, method="bridge")
#saveRDS(bridge, "bridge.rds")
bridge<- readRDS("bridge.rds")
pred_bridge <- round(predict(bridge, newdata=test_set),1)
```

Random Forest
```{r}
#rf <- train(PremiumPrice ~., data=data_train, trControl=train_control, method="rf")
#saveRDS(rf, "rf.rds")
rf<- readRDS("rf.rds")
pred_rf <- round(predict(rf, newdata=test_set),1)
```

Support Vector Machine
```{r}
#svm <- train(PremiumPrice ~., data=data_train, trControl=train_control, method="svmLinear")
#saveRDS(svm, "svm.rds")
svm<- readRDS("svm.rds")
pred_svm <- round(predict(svm, newdata=test_set),1)
```

Glmnet is a package that fits generalized linear and similar models via penalized maximum likelihood.
```{r}
#glmnet <- train(PremiumPrice~., data=data_train, trControl=train_control, method="glmnet")
#saveRDS(glmnet, "glmnet.rds")
glmnet<- readRDS("glmnet.rds")
pred_glmnet <- round(predict(glmnet, newdata=test_set),1)
```


summary regression metrics for each model train set
```{r}
resamps <- resamples(list(knn = knn,
                          bridge = bridge,
                          rf = rf,
                          SVM = svm,
                          glmnet = glmnet))
summary(resamps)
```
summary regression metrics for each model test set
```{r}
df_me <- data.frame (Method  = c(0),
                  RSMERsquared = c(0),
                  Rsquared = c(0),
                  MAE = c(0))
df_me

test_pred <- predict(rf, newdata = test_set)
result <-postResample(test_pred, test_set$PremiumPrice)
df_me<-rbind(df_me,c("rf",result["RMSE"],result["Rsquared"],result["MAE"]))

test_pred <- predict(glmnet, newdata = test_set)
result <-postResample(test_pred, test_set$PremiumPrice)
df_me<-rbind(df_me,c("glmnet",result["RMSE"],result["Rsquared"],result["MAE"]))

test_pred <- predict(svm, newdata = test_set)
result <-postResample(test_pred, test_set$PremiumPrice)
df_me<-rbind(df_me,c("svm",result["RMSE"],result["Rsquared"],result["MAE"]))

test_pred <- predict(bridge, newdata = test_set)
result <-postResample(test_pred, test_set$PremiumPrice)
df_me<-rbind(df_me,c("bridge",result["RMSE"],result["Rsquared"],result["MAE"]))

test_pred <- predict(knn, newdata = test_set)
result <-postResample(test_pred, test_set$PremiumPrice)
df_me<-rbind(df_me,c("knn",result["RMSE"],result["Rsquared"],result["MAE"]))
df_me
```
plot each variable importance
```{r}
x<-varImp(rf)
```

```{r}
plot(x)
```

code inference 
```{r}
Age <- 40
Weight <- 60
AnyTransplants <- 0
NumberOfMajorSurgeries <-0
AnyChronicDiseases <-0
Height <-0
HistoryOfCancerInFamily<-0
BloodPressureProblems<-0
Diabetes<-0
KnownAllergies<-0
infe_df <- data.frame(
  Age,
  Weight,
  AnyTransplants,
  NumberOfMajorSurgeries,
  AnyChronicDiseases,
  Height,
  HistoryOfCancerInFamily,
  BloodPressureProblems,
  Diabetes,
  KnownAllergies
)
infe_df
prediction <- predict(rf, newdata = infe_df)
```

```{r}
rf<- readRDS("rf.rds")
pred_rf <- round(predict(rf, newdata=test_set),1)
prediction
```


